Efficient evaluation of threshold queries of derived fields in a numerical simulation database

### 2015-01-15 paper.tex
Minor fixes.

{\bf Application-aware cache for query results:} A central part of the evaluation strategy for threshold queries that we have developed is the 
introduction of an application-aware cache
for query results (Fig. \ref{fig:cache_diagram}). The results of these queries are small compared to the amount of data that need to be examined and the
results can be used to answer subsequent queries as long as they are within the same region and specify the same or higher threshold. Each database node 
has a local cache. Cache entries are indexed by the field, time-step, spatial region and the threshold requested. We use a least recently
used cache replacement policy. All modifications of and queries to the cache are executed within a transaction with snapshot isolation level to
avoid dirty-reads or an inconsistent view of the cache.

>>>>

\vspace{5pt}
{\bf Application-aware cache for query results:} A central part of the evaluation strategy for threshold queries that we have developed is the 
introduction of an application-aware cache
for query results (Fig. \ref{fig:cache_diagram}). The results of these queries are small compared to the amount of data that need to be examined and the
results can be used to answer subsequent queries as long as they are within the same region and specify the same or higher threshold. Each database node 
has a local cache. Cache entries are indexed by the field, time-step, spatial region and the threshold requested. We use a least recently
used cache replacement policy. All modifications of and queries to the cache are executed within a transaction with snapshot isolation level to
avoid dirty-reads or an inconsistent view of the cache.
